### 2016-02-28 config/styles.inc.tex
Import LRM Hinf files

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize}}
\pgfplotsset{every axis post/.style={unbounded coords=jump}}
\pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}

@@

@@

\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

@@

>>>>

\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
\pgfplotsset{every axis post/.style={unbounded coords=jump}}

@@

\definecolor{first}{named}{TangoScarletRed2}
\definecolor{second}{named}{TangoOrange2}
\definecolor{third}{named}{TangoChameleon3}
\definecolor{fourth}{named}{TangoSkyBlue3}
\definecolor{fifth}{named}{TangoPlum1}
\definecolor{sixth}{named}{TangoChocolate2}

@@

\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

@@

%% interpolation figure

\pgfplotsset{continuous/.style={line width=0.75pt,mark options={solid},mark size=3pt}}
\pgfplotsset{first/.style={color=first,continuous}}
\pgfplotsset{second/.style={color=second,continuous}}
\pgfplotsset{third/.style={color=third,continuous}}
\pgfplotsset{fourth/.style={color=fourth,continuous}}
\pgfplotsset{fifth/.style={color=fifth,continuous}}
\pgfplotsset{sixth/.style={color=sixth,continuous}}

\pgfplotsset{range/.style={line width=0.75pt,mark options={solid},mark=|,mark size=2pt}}

\pgfplotsset{atGrid/.style={mark=*,mark size=1.5pt,only marks,mark options={solid}}}
\pgfplotsset{firstgrid/.style={atGrid,color=first}}
\pgfplotsset{secondgrid/.style={atGrid,color=second}}
\pgfplotsset{thirdgrid/.style={atGrid,color=third}}
\pgfplotsset{fourthgrid/.style={atGrid,color=fourth}}
\pgfplotsset{fifthgrid/.style={atGrid,color=fifth}}
\pgfplotsset{sixthgrid/.style={atGrid,color=sixth}}

%%
